A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-05 deprecated.tex
Reduce the length of our DM description

>>>>

% move belows to background-archi
The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. Connections of participants are built via brokers, which can avert sensitive information leaks in order to establish communication. Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities, for instance, the services are paralyzed if the server is crashed or attacked. Therefore, we adopted decentralized pub/sub model with no organization holding brokers. Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.

Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated. This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality. Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.

### 2020-05-05 paper.tex
Reduce the length of our DM description

\subsection{Towards Decentralized Data Marketplace}
In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly  Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}.

The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.  Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities of centralized pub/sub models, for instance, central point of failure, if the centralized server is crashed or attacked, the services will not be available. Therefore, we adopted decentralized pub/sub with no organization holding brokers, and the brokers are only responsible for data transmission and agreement establishment. Furthermore, the communication between entities is built via brokers, which prevents sensitive information leaks. Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.

Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated. This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality. Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.

Another key component MAM is viewed as the data storage of data marketplace which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the  disconnection does not exist, participants can retrieve the authoraized data streams anytime.

\subsection{Choice of Data Storage}
In our proposed architecture, MAM is the data storage where the data assets is reserved. However, the operations of MAM are time-consuming for IoT devices, which are evaluated in Section CITE-EVALUATION-SECTION. We assume the data assets are stored in distributed data storage systems built on top of peer-to-peer (P2P) networks maintained by multiple nodes, which avoid the central point failure and security issues of central databases. Among the existing distributed storage studied in Section CITE-RELATED-WORK, different backup mechanisms and access controls strategies are proposed, however, the keys managed by participant is hard to be as small as possible especially for data streams, which is one of the scalability requirement of data marketplace mentioned above.

>>>>

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-effieciency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key management. The three keys of decentralized data marketplace meet the requirements metioned previously.

\subsection{Choice of Data Storage}
In our proposed architecture, MAM is the data storage where the data assets is reserved. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.
